Human judgement forecasting of COVID-19 in the UK

### 2024-02-10 manuscript/manuscript.tex
Make small additions to the manuscript

Every week, we submitted an ensemble of individual forecasts to the European Forecast Hub. In contrast to the ensemble of human forecasts described in \citet{bosseComparingHumanModelbased2022}, we used the quantile-wise median, rather than the quantile-wise mean to combine predictions, drawing upon insights gained from the COVID-19 Forecast Hubs \citep{rayComparingTrainedUntrained2022}. 
We submitted three different ensembles to the Hub: The first one, "epiforecasts-EpiExpert\_direct" (here called "direct crowd forecast" or "crowd-direct") was a quantile-wise median ensemble of all the direct forecasts. "epiforecasts-EpiExpert\_Rt" (here called "$R_t$ forecast" or "crowd-rt") was a median ensemble of all forecasts made through the $R_t$ interface. "epiforecasts-EpiExpert" (here called "combined crowd ensemble" or "crowd-ensemble") was a median ensemble of all forecasts together. A participant could enter the combined crowd ensemble twice if they had submitted both a direct and an $R_t$ forecast. Before creating the ensemble, we deleted forecasts that were clearly the result of a user or software error (such as forecasts that were zero everywhere).

@@

@@

It is plausible to hypothesise that the default baseline shown to forecasters in the app may influence their predictions. One could also interpret the $R_t$-forecast as a way of showing a different baseline forecast to the forecaster compared to the direct forecast. In our study, the default was a naive forecast with the median equal to the last value and uncertainty equal to the standard deviation of the last four changes in weekly log values. \cite{bosseComparingHumanModelbased2022} did not fnd conclusive evidence to that effect, but also did not analyse the question in detail. We suggest further research be done into potential priming effects that a default forecast can have on users.

@@

\subsection*{Acknowledgements}
We thank all forecasters for their participation and want to congratulate the three winners of the forecasting challenge: Russell Bradshaw, Sebastian Funk (an author of this study), and Akira Endo. All winners donated their prizes.

>>>>

Every week, we submitted an ensemble of individual forecasts to the European Forecast Hub. In contrast to the ensemble of human forecasts described in \citet{bosseComparingHumanModelbased2022}, we used the quantile-wise median, rather than the quantile-wise mean to combine predictions, drawing upon insights gained from the COVID-19 Forecast Hubs \citep{rayComparingTrainedUntrained2022}. 
We submitted three different ensembles to the Hub: The first one, "epiforecasts-EpiExpert\_direct" (here called "direct crowd forecast" or "crowd-direct") was a quantile-wise median ensemble of all the direct forecasts. "epiforecasts-EpiExpert\_Rt" (here called "$R_t$ forecast" or "crowd-rt") was a median ensemble of all forecasts made through the $R_t$ interface. "epiforecasts-EpiExpert" (here called "combined crowd ensemble" or "crowd-ensemble") was a median ensemble of all forecasts together. A participant could enter the combined crowd ensemble twice if they had submitted both a direct and an $R_t$ forecast. Before creating the ensemble, we deleted forecasts that were clearly the result of a user or software error (such as forecasts that were zero everywhere). Our combined crowd ensemble, "epiforecasts-EpiExpert", but not the other two, entered the official European COVID-19 Forecast Hub ensemble ("EuroCOVIDhub-ensemble").

@@

Importantly, in this study our combined crowd ensemble ("epiforecasts-EpiExpert") contributed to the European Forecast Hub ensemble. This in contrast to the study by \citet{bosseComparingHumanModelbased2022}, where they compared crowd forecasts against a hypothetical ensemble excluding the crowd forecasts. In the original study, including the crowd forecasts improved the Hub ensemble on average (however, the overall number of models included in the German and Polish Hub ensemble was smaller than the number of models in the European Forecast Hub ensemble). In our study, comparisons between our crowd ensembles and the Forecast Hub ensemble are therefore confounded by the fact the combined crowd ensemble was included in the Forecast Hub ensemble, possibly leading us to underestimate differences between the two.

@@

It is plausible to hypothesise that the default baseline shown to forecasters in the app may influence their predictions. One could also interpret the $R_t$-forecast as a way of showing a different baseline forecast to the forecaster compared to the direct forecast. In our study, the default was a naive forecast with the median equal to the last value and uncertainty equal to the standard deviation of the last four changes in weekly log values. \cite{bosseComparingHumanModelbased2022} did not find conclusive evidence to that effect, but also did not analyse the question in detail. We suggest further research be done into potential priming effects that a default forecast can have on users.

@@

\subsection*{Acknowledgements}
We thank all forecasters for their participation and want to congratulate the three winners of the forecasting challenge: Russell Bradshaw, Sebastian Funk (an author of this study), and Akira Endo. All winners donated their prizes. We also thank Daniel J. McDonald for his kind and thoughtful review which has helped improve the manuscript substantially.
